Hydra Battles and Cie

### 2021-05-11 doc/chapter-primrec.tex
chantier
corrections of typos
minor changes

@@

@@

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}.}

@@

Notation "'v_apply' f v" := (evalList _ v f) ( at level 10, f at level 9).

Example Ex2 : forall (f: naryFunc 2) x y,
    v_apply f (x::y::nil) = f x y.
Proof.   intros; now cbn. Qed.

Example Ex4 : forall (f: naryFunc 4) x y z t,
    v_apply f (x::y::z::t::nil) = f x y z t.
Proof.  intros; now cbn. Qed.
\end{Coqsrc}

@@

\begin{remark}
It is easy to prove that any unary function which dominatates \texttt{fun n => Ack n n} fails to be primitive recursive. We use an instance of \texttt{majorAnyPR} for unary functions.
\vspace{4pt}
\noindent

>>>>

\begin{remark}
 The statements above can be rewritten in a more uniform way:

 \begin{quote}
   For $m\in 1..4$, $\texttt{Ack}\,m\,n = f_m\,(n+3)-3$, where 
   \begin{align*}
   f_1(n)=&\,n+2 \\
   f_2(n)=&\,n\times 2\\
   f_3(n)=&\,2^n\\
   f_4(n)=&\,2^{2^{\dots^2}}\quad(n\;\textit{levels})
   \end{align*}
 \end{quote}
\end{remark}

@@

\vspace{4pt}

@@

\vspace{4pt}

\noindent
\emph{From \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}.}

@@

Notation "'v_apply' f v" := (evalList _ v f) 
     (at level 10, f at level 9).

Example Ex2: forall (f: naryFunc 2) x y,
    v_apply f (x::y::nil) = f x y.
Proof.   intros; now cbn. Qed.

Example Ex4: forall (f: naryFunc 4) x y z t,
    v_apply f (x::y::z::t::nil) = f x y z t.
Proof.  intros; now cbn. Qed.
\end{Coqsrc}

@@

\begin{remark}
It is easy to prove that any unary function which dominatates \texttt{fun n => Ack n n} fails to be primitive recursive. We use an instance of \texttt{majorAnyPR} for unary functions.

\vspace{4pt}
\noindent
